Linear Ordered Attribute Grammar scheduling using SAT-solving

### 2014-10-14 paper/paper.tex
Cite PEPM paper in introduction

@@

The class of \emph{ordered attribute grammars} \cite{kastens80} is a well-known subclass of attribute grammars for which a polynomial time scheduling algorithm exists. However, despite what the name suggests there exist attribute grammars for which a static evaluation order can be found that do not belong to the class of ordered attribute grammars. In our work on compiler construction we often encountered this situation, giving rise to the need of other scheduling algorithms \cite{bransen2012}. We therefore look at the class of \emph{linear ordered attribute grammars} in this paper, which is the largest class of attribute grammars for which a static evaluation order can be found. The problem of statically finding such evaluation order is known to be NP-complete \cite{engelfriet82}.

@@

\Jeroen{todo in intro: cite Minisat?, cite Binsbergen:2015 (PEPM)}

@@

\bibliographystyle{splncs}
\bibliography{biblio}

>>>>

% Handle citing "Van Binsbergen" correctly...
\DeclareRobustCommand{\VAN}[3]{#2}

@@

The class of \emph{ordered attribute grammars} \cite{kastens80} is a well-known subclass of attribute grammars for which a polynomial time scheduling algorithm exists. However, despite what the name suggests there exist attribute grammars for which a static evaluation order can be found that do not belong to the class of ordered attribute grammars. In our work on compiler construction we often encountered this situation, giving rise to the need of other scheduling algorithms \cite{bransen2012,Binsbergen:2015}. We therefore look at the class of \emph{linear ordered attribute grammars} in this paper, which is the largest class of attribute grammars for which a static evaluation order can be found. The problem of statically finding such evaluation order is known to be NP-complete \cite{engelfriet82}.

@@

\Jeroen{todo in intro: cite Minisat?}

@@

\DeclareRobustCommand{\VAN}[3]{#3}
\bibliographystyle{splncs}
\bibliography{biblio}
